%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Thanks
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\chapter{Acknowledgements}
\begin{it}



The past six months have been an exciting journey, dedicated to the last step in finishing my master Data Science at Ynov Aix-en-Provence: writing this thesis. I would like to express my sincere gratitude to those who helped me during this period.

First of all, I would like to thank Pascal Alanche for giving me the opportunity to work at Arpège SAS a Rohde \& Schwarz company during my 3 years of apprenticeship. It was a great experience to be part of the R\&D team and participate in the many interesting projects of the company. I have met a lot of remarkable people who taught me valuable knowledge about geostationary satellites and high-frequency radio communication. I would like to thank my supervisor from Ynov, Renaud Angles, for his guidance throughout the research project. His feedback, whether it was enthusiastic or critical, helped me to structure and improve this thesis and to continue the project at tough points.

Likewise, I would like to thank Olivier Gimenez, Oksana Grente, Anna Chaine, Lucile Marescot from the CNRS and ONCFS for their invaluable information about the context of camera-trap and wildlife monitoring, as well as the introduction to ecology research.

My gratitude also goes to the people of the open-source world from the people sharing publicly datasets, to the people on the algorithm side, developing amazing framework and making fantastic tutorials, thanks Github, Microsoft, Google, especially in my case at least.

Finally, I would like to express my gratitude to my parents and family for their support and wisdom throughout my thesis. Especially my brother Romain who guided me through the difficulties encountered on the technical parts.

I hope that you will enjoy reading the current research. If you have any questions or comments, please do not hesitate to contact me.

\end{it}